### 2017-03-30 paper/intro.tex
pass on abstract; minor change in intro

At large organizations, the alternative of renting cloud
services\footnote{List of popular hosting cloud services:
  \url{https://clutch.co/cloud}} or even building proprietary
infrastructures to running tests is a legitimate approach to mitigate
the regression testing problem.  However, for projects with low
budgets and yet relatively heavy testing workloads, this solution may
not be economically viable.  For these cases, the use of commodity
hardware (\eg{}, existing workstations), emerges as an attractive
solution for running tests.  Furthermore, the proliferation of
multi-core CPUs and the increasing popularization of testing
frameworks and build systems, which today provide mature support for
parallelization, enable test execution speedups through increased CPU
usage~(see Section~\ref{sec:modes}).  These two elements~---~demand
for cost-effective test execution and supply of testing
infrastructure~---~led us to investigate if and how parallelization
features from testing frameworks and build systems are used in
practice.

>>>>

At large organizations, the alternative of renting cloud
services\footnote{List of popular hosting cloud services:
  \url{https://clutch.co/cloud}} or even building proprietary
infrastructures to running tests is a legitimate approach to mitigate
the regression testing problem.  However, for projects with low
budgets and yet relatively heavy testing workloads, this solution may
not be economically viable.  For these cases, the use of commodity
hardware (\eg{}, existing workstations), emerges as an attractive
solution for running tests.  Furthermore, the proliferation of
multi-core CPUs and the increasing popularization of testing
frameworks and build systems, which today provide mature support for
parallelization, enable test execution speedups through increased CPU
usage~(see Section~\ref{sec:modes}).  These two elements~---~demand
for cost-effective test execution and supply of testing
infrastructure~---~led us to investigate the usage of parallelization
features from testing frameworks and build systems in public
open-source projects.
